Object-based Auditory Scenes Similarity Retrieval and Classification With Scattering Transforms

### 2016-07-08 paper/structureScene.tex
update IV. C

This strategy is already widespread in the literature.
For instance, we should note that \cite{roma2013}, who secured the first place in the 2013 edition of the DCASE challenge, rely on cepstral descriptors computed up to a cutoff frequency as small as $\xi_{1,\max}  = 900\,\mathrm{Hz}$ instead of the more conventional value of $16\,\mathrm{kHz}$.

\subsection{Logarithmic compression}
Many algorithms in pattern recognition, including nearest neighbor classifiers and support vector machines, tend to work best when all features follow a standard normal distribution across all training instances.
Yet, because of the complex modulus nonlinearity, scattering coefficients are nonnegative by design, and their distribution is typically skewed towards the right \ml{c'est quoi la droite, sans figure c'est pas facile de voir de quoi tu parles}.
This issue can however be addressed by applying to all coefficients a pointwise concave transformation, \eg logarithmic, hence reducing skewness.

@@

In particular, logarithmic compression is ubiquitous in audio signal processing, as it is corroborated by the Weber-Fechner law in psychoacoustics, which states that the sensation of loudness is roughly proportional to the logarithm of the acoustic pressure.
In the context of auditory scenes, we must also recall that the measured amplitude of sound sources often decays polynomially with the distance to the binaural microphone, which is a spurious factor a variability to the task of auditory scene classification.
Logarithmic compression can linearize this dependency, which arguably facilitates the construction of a powerful invariant at the classifier stage.

>>>>

This strategy is already widespread in the literature.
For instance, we should note that \cite{roma2013}, who secured the first place in the 2013 edition of the DCASE challenge, rely on cepstral descriptors computed up to a cutoff frequency as small as $\xi_{1,\max}  = 900\,\mathrm{Hz}$ instead of the more conventional value of $16\,\mathrm{kHz}$.
\vl{Qu'en penses-tu ML ?}

\subsection{Logarithmic compression}
Many algorithms in pattern recognition, including nearest neighbor classifiers and support vector machines, tend to work best when all features follow a standard normal distribution across all training instances.
Yet, because of the complex modulus nonlinearity, scattering coefficients are nonnegative by design.
It appears empirically that their distribution is skewed towards the right, which means that the tail towards greater values is longer than the tail towards lower values.
However, skewness can be reduced by applying to all coefficients a pointwise concave transformation, \eg logarithmic.
Figure \ref{fig:histograms} shows the distribution of an arbitrarily chosen scattering coefficient over the DCASE 2013 dataset, before and after logarithmic compression.
\vl{Qu'en penses-tu ML ?}

@@

The application of the pointwise logarithm to magnitude spectra is ubiquitous in audio signal processing.
Indeed, it is corroborated by the Weber-Fechner law in psychoacoustics, which states that the sensation of loudness is roughly proportional to the logarithm of the acoustic pressure.
In the context of auditory scenes, we must also recall that the measured amplitude of sound sources often decays polynomially with the distance to the binaural microphone, which is a spurious factor a variability to the task of auditory scene classification.
Logarithmic compression can linearize this dependency, which arguably facilitates the construction of a powerful invariant at the classifier stage.
